Formalization of Network Flow Algorithms

### 2017-02-28 paper/root.tex
diagram of all benchmarks
final diagrams

  \begin{figure}[!h]
  \begin{tikzpicture}[thick,scale=.8, every node/.style={scale=1}] %change the scales if you like to reduce the size
    \begin{axis}[
      %title={Benchmark of the Edmonds-Karp algorithm},
        axis x line*= bottom,
        axis y line*= left,
        xmode = log,
        ymode = log,
%         xlabel = Number of vertices in the network,
%         ylabel = Execution time in seconds, 
        xtick = {0,1000,...,5000},
        ytick = {0.01,0.1,1,10},
        xticklabels = {$1000$, $2000$, $3000$, $4000$, $5000$},
        yticklabels = {$0.01$,$0.1$,$1$,$10$}, 
        smooth,
        cycle list name = black white,
        legend style = { 
          at={(0.59,0.4)}, 
            anchor=north west,
            draw=black, 
            fill= white,
            align=left
        }
    ]

    %start data for plotting
      \addplot table {
        1000 .027   
        1500 .124  
        2000 .299  
        2500 .665  
        3000 1.335 
        3500 2.526 
        4000 3.111 
        4500 6.917 
        5000 7.743 
        5500 10.452    
      }; \addlegendentry{SML, sparse};

      \addplot table {
        1000 .016   
        1500 .049   
        2000 .168  
        2500 .453  
        3000 .842  
        3500 1.524 
        4000 2.136 
        4500 3.438 
        5000 4.734 
        5500 6.369     
      }; \addlegendentry{Java, sparse};
    %end data for plotting
    \end{axis}
  \end{tikzpicture}
%
  \begin{tikzpicture}[thick,scale=.8, every node/.style={scale=1}] %change the scales if you like to reduce the size
    \begin{axis}[
      %title={Benchmark of the Edmonds-Karp algorithm},
        axis x line*= bottom,
        axis y line*= left,
        xmode = log,
        ymode = log,
%         xlabel = Number of vertices in the network,
%         ylabel = Execution time in seconds, 
        xtick = {0,1000,1100,...,1400},
        ytick = {2,4,...,10},
        xticklabels = {$1000$, $1100$, $1200$, $1300$, $1400$}, 
        yticklabels = {$2$, $4$,$6$,$8$,$10$}, 
        smooth,
        cycle list name = black white,
        legend style = { 
          at={(0.59,0.4)}, 
            anchor=north west,
            draw=black, 
            fill= white,
            align=left
        }
    ]

    %start data for plotting
      \addplot table {
        1000 3.328 
        1050 3.345 
        1100 4.841 
        1150 5.036 
        1200 5.840 
        1250 6.858 
        1300 7.651 
        1350 8.950 
        1400 8.398 
        1450 10.769     
      }; \addlegendentry{SML, dense};

      \addplot table {
        1000 4.141 
        1050 4.778 
        1100 5.465 
        1150 6.248 
        1200 7.128 
        1250 8.137 
        1300 9.864 
        1350 11.008
        1400 11.902
        1450 13.365     
      }; \addlegendentry{Java, dense};
    %end data for plotting
    \end{axis}
  \end{tikzpicture}

%   \centering    
%   \begin{tikzpicture}[thick,scale=1, every node/.style={scale=1}] %change the scales if you like to reduce the size
%     \begin{axis}[
%       %title={Benchmark of the Edmonds-Karp algorithm},
%         axis x line*= bottom,
%         axis y line*= left,
%         xmode = log,
%         ymode = log,
%         xlabel = Number of vertices in the network,
%         ylabel = Execution time in milliseconds, %in milliseconds, modify the scale for lables
%         xtick = {0,1000,...,5000},
% %         ytick = data,
%         xticklabels = {$1000$, $2000$, $3000$, $4000$, $5000$}, %corresponds to the first column in {SML, Sparse}
% %         yticklabels = {$0.2$, $1.4$, $4.9$, $9.2$, $23.6$}, %corresponds to the second column in {SML, Sparse}
%         smooth,
%         cycle list name = black white,
%         legend style = { 
%           at={(0.59,0.4)}, 
%             anchor=north west,
%             draw=black, 
%             fill= white,
%             align=left
%         }
%     ]
%     
%     %start data for plotting
%       \addplot table {
%         1000 27   
%         1500 124  
%         2000 299  
%         2500 665  
%         3000 1335 
%         3500 2526 
%         4000 3111 
%         4500 6917 
%         5000 7743 
%         5500 10452    
%       }; \addlegendentry{SML, sparse};
% 
%       \addplot table {
%         1000 16   
%         1500 49   
%         2000 168  
%         2500 453  
%         3000 842  
%         3500 1524 
%         4000 2136 
%         4500 3438 
%         5000 4734 
%         5500 6369     
%       }; \addlegendentry{Java, sparse};
% 
%       \addplot table {
%         1000 3328 
%         1050 3345 
%         1100 4841 
%         1150 5036 
%         1200 5840 
%         1250 6858 
%         1300 7651 
%         1350 8950 
%         1400 8398 
%         1450 10769     
%       }; \addlegendentry{SML, dense};
% 
%       \addplot table {
%         1000 4141 
%         1050 4778 
%         1100 5465 
%         1150 6248 
%         1200 7128 
%         1250 8137 
%         1300 9864 
%         1350 11008
%         1400 11902
%         1450 13365     
%       }; \addlegendentry{Java, dense};
%     %end data for plotting
%     \end{axis}
%   \end{tikzpicture}

%   \center{\footnotesize The x-axis shows the number of nodes, the y axis the execution time in seconds.}
  \caption{Benchmark of different implementations. The x-axis shows the number of nodes, the y axis the execution time in seconds.}\label{fig:benchmark}
  \end{figure}

>>>>

  \begin{figure}[!h]
  \begin{tikzpicture}[thick,scale=.8, every node/.style={scale=1}] %change the scales if you like to reduce the size
    \begin{axis}[
      %title={Benchmark of the Edmonds-Karp algorithm},
        axis x line*= bottom,
        axis y line*= left,
        xmode = log,
        ymode = log,
%         xlabel = Number of vertices in the network,
%         ylabel = Execution time in seconds, 
        xtick = {0,1000,...,5000},
        ytick = {0.01,0.1,1,10},
        xticklabels = {$1000$, $2000$, $3000$, $4000$, $5000$},
        yticklabels = {$0.01$,$0.1$,$1$,$10$}, 
        smooth,
        cycle list name = black white,
        legend style = { 
          at={(0.515,0.24)}, 
            anchor=north west,
            draw=black, 
            fill= white,
            align=left
        }
    ]

    %start data for plotting
      \addplot table {
        1000 .024   
        1500 .098  
        2000 .211  
        2500 .693  
        3000 2.014 
        3500 3.153 
        4000 3.679 
        4500 8.364 
        5000 10.328 
        5500 11.749    
      }; \addlegendentry{edka-SML, sparse};

      \addplot table {
        1000 .024   
        1500 .054   
        2000 .103  
        2500 .399  
        3000 .719  
        3500 1.362 
        4000 2.036 
        4500 3.334 
        5000 4.785 
        5500 6.079     
      }; \addlegendentry{edka-Java, sparse};

      \addplot table {
        1000 .005   
        1500 .013  
        2000 .024  
        2500 .037  
        3000 .066 
        3500 .077 
        4000 .096 
        4500 .146 
        5000 .194 
        5500 .192    
      }; \addlegendentry{prpu-SML, sparse};
    %end data for plotting
    \end{axis}
  \end{tikzpicture}
%
  \begin{tikzpicture}[thick,scale=.8, every node/.style={scale=1}] %change the scales if you like to reduce the size
    \begin{axis}[
      %title={Benchmark of the Edmonds-Karp algorithm},
        axis x line*= bottom,
        axis y line*= left,
        xmode = log,
        ymode = log,
%         xlabel = Number of vertices in the network,
%         ylabel = Execution time in seconds, 
        xtick = {0,1000,1100,...,1400},
        ytick = {1,4,...,16},
        xticklabels = {$1000$, $1100$, $1200$, $1300$, $1400$}, 
        yticklabels = {$1$,$4$,$8$,$12$,$16$}, 
        smooth,
        cycle list name = black white,
        legend style = { 
          at={(0.53,0.6)}, 
            anchor=north west,
            draw=black, 
            fill= white,
            align=left
        }
    ]

    %start data for plotting
      \addplot table {
        1000	2.794
        1050	2.9
        1100	4.405
        1150	4.435
        1200	5.232
        1250	6.029
        1300	7.699
        1350	8.91
        1400	7.225
        1450	10.042 
      }; \addlegendentry{edka-SML, dense};

      \addplot table {
        1000	3.982
        1050	4.463
        1100	5.278
        1150	6.27
        1200	6.939
        1250	7.953
        1300	9.392
        1350	10.317
        1400	14.71
        1450	13.11  
      }; \addlegendentry{edka-Java, dense};

      \addplot table {
        1000	0.074
        1050	0.059
        1100	0.068
        1150	0.075
        1200	0.102
        1250	0.085
        1300	0.096
        1350	0.103
        1400	0.088
        1450	0.114  
      }; \addlegendentry{prpu-SML, dense};
    \end{axis}
  \end{tikzpicture}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
  \begin{tikzpicture}[thick,scale=.8, every node/.style={scale=1}] %change the scales if you like to reduce the size
    \begin{axis}[
      %title={Benchmark of the Edmonds-Karp algorithm},
        axis x line*= bottom,
        axis y line*= left,
        xmode = log,
        ymode = log,
%         xlabel = Number of vertices in the network,
%         ylabel = Execution time in seconds, 
        xtick = {3000, 6000, 10500, 13500, 16500},
        ytick = {0.1,1,10,50,100},
        xticklabels = {$3k$, $6k$, $10k$, $13k$, $16k$},
        yticklabels = {$\text{\ \,}0.1$,$1$,$10$,$50$,$100$}, 
        smooth,
        cycle list name = black white,
        legend style = { 
          at={(0.53,0.24)}, 
            anchor=north west,
            draw=black, 
            fill= white,
            align=left
        }
    ]

    %start data for plotting

      \addplot table {
        3000	1.185
        4500	3.524
        6000	6.457
        7500	11.509
        9000	17.529
        10500	26.185
        12000	36.828
        13500	48.614
        15000	86.449
        16500	89.661
      }; \addlegendentry{prpu-SML, wash};

      \addplot table {
        3000	0.906
        4500	2.708
        6000	5.083
        7500	8.792
        9000	12.951
        10500	19.075
        12000	27.466
        13500	35.964
        15000	61.839
        16500	67.039
      }; \addlegendentry{prpu-C++, wash};

      \addplot table {
        3000	0.006
        4500	0.015
        6000	0.029
        7500	0.042
        9000	0.063
        10500	0.084
        12000	0.115
        13500	0.144
        15000	0.183
        16500	0.223
      }; \addlegendentry{prpu-C, wash};
    %end data for plotting
    \end{axis}
  \end{tikzpicture}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
  \begin{tikzpicture}[thick,scale=.8, every node/.style={scale=1}] %change the scales if you like to reduce the size
    \begin{axis}[
      %title={Benchmark of the Edmonds-Karp algorithm},
        axis x line*= bottom,
        axis y line*= left,
        xmode = log,
        ymode = log,
%         xlabel = Number of vertices in the network,
%         ylabel = Execution time in seconds, 
        xtick = {0,1000,1100,...,1400},
        ytick = {0.01, 0.1, 0.2, 0.5, 1},
        xticklabels = {$1000$, $1100$, $1200$, $1300$, $1400$}, 
        yticklabels = {$0.01$, $0.1$,$0.2$,$0.5$,$1$}, 
        smooth,
        cycle list name = black white,
        legend style = { 
          at={(0.52,0.24)}, 
            anchor=north west,
            draw=black, 
            fill= white,
            align=left
        }
    ]

    %start data for plotting
      \addplot table {
        1000	0.141
        1050	0.202
        1100	0.157
        1150	0.273
        1200	0.24
        1250	0.408
        1300	0.465
        1350	1.416
        1400	0.657
        1450	0.806
      }; \addlegendentry{prpu-SML, acnet};

      \addplot table {
        1000	0.121
        1050	0.17
        1100	0.123
        1150	0.216
        1200	0.197
        1250	0.237
        1300	0.298
        1350	0.621
        1400	0.399
        1450	0.486
      }; \addlegendentry{prpu-C++, acnet};

      \addplot table {
        1000	0.056
        1050	0.09
        1100	0.069
        1150	0.106
        1200	0.09
        1250	0.152
        1300	0.163
        1350	0.176
        1400	0.223
        1450	0.209
      }; \addlegendentry{prpu-C, acnet};
    \end{axis}
  \end{tikzpicture}
  %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
  \begin{tikzpicture}[thick,scale=.8, every node/.style={scale=1}] %change the scales if you like to reduce the size
    \begin{axis}[
      %title={Benchmark of the Edmonds-Karp algorithm},
        axis x line*= bottom,
        axis y line*= left,
        xmode = log,
        ymode = log,
%         xlabel = Number of vertices in the network,
%         ylabel = Execution time in seconds, 
        xtick = {16000,19000,23000,27000,30000},
        ytick = {0.1,1,5,10,25},
        xticklabels = {$16k$, $19k$, $23k$, $27k$, $30k$}, 
        yticklabels = {$\text{\ \,}0.1$, $1$,$5$,$10$,$25$}, 
        smooth,
        cycle list name = black white,
        legend style = { 
          at={(0.49,0.6)}, 
            anchor=north west,
            draw=black, 
            fill= white,
            align=left
        }
    ]

    %start data for plotting
      \addplot table {
        16000	3.602
        17600	4.223
        19200	4.839
        20800	8.201
        22400	8.273
        24000	13.426
        25600	10.089
        27200	15.889
        28800	16.431
        30400	21.437
      }; \addlegendentry{prpu-SML, genrmf};

      \addplot table {
        16000	4.51
        17600	4.804
        19200	5.899
        20800	8.052
        22400	8.448
        24000	11.555
        25600	8.878
        27200	13.999
        28800	12.99
        30400	13.791
      }; \addlegendentry{prpu-C++, genrmf};

      \addplot table {
        16000	0.009
        17600	0.012
        19200	0.015
        20800	0.021
        22400	0.021
        24000	0.019
        25600	0.023
        27200	0.028
        28800	0.026
        30400	0.026
      }; \addlegendentry{prpu-C, genrmf};
    \end{axis}
  \end{tikzpicture}
  \caption{Benchmark of different implementations. The x-axis shows the number of nodes, the y axis the execution time in seconds.}\label{fig:benchmark}
  \end{figure}
